The Types and Driving Forces of Modifications in the Evolution of an API

### 2015-05-12 thesis/paper.tex
Re-wrote meth

\subsection{Data Collection} \label{data_collection}  %Review 1 or 2 more times (John first)
%Intro to code inspection
The data were collected primarily through inspections of the source code and the analysis of accompanying documentation. The source code was comprised of the two API versions previously mentioned. Each version of the API had its own respective documentation, including example code, a library description and a basic development manual.

@@

\subsection{Data Analysis} \label{data_analysis}
%Intro and summary
The data analysis was conducted in two major phases \cite{andersson2007spiral}. The aim of the first phase was to generate hypotheses \cite{seaman1999qualitative} and to formulate clear research questions. It was during this phase that the analysis of the API code and documentation was carried out. The second phase included analysis of the interviews, the goal of which was to confirm the hypotheses \cite{seaman1999qualitative} that were formulated in the first phase. Both phases were performed iteratively, together with the data collection. This created the opportunity to improve the process of analysis as the study progressed, as well as, allowing the study to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase \cite{andersson2007spiral}.

%Grounded Theory
The process used for analysing the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.
%Codes
Each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
%Concepts
Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were categorised on their own.
%Categories
These concepts were then grouped into categories based on common patterns between the concepts.
%Theory
These categories were then used to identify the most notable trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.

%RQ1
The categories identified previously were then classified according to the software maintenance categories \cite{chapin2001types}. The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified categories were given a main category of maintenance and a secondary category, if appropriate. This material was then used as a basis for answering \textbf{RQ1}.

%Description of interview analysis
The results of the interview were analysed and categorised in the same way that our identified changes had been. Validation of our findings, by comparing our categorisation against the interviewee's categorisation, was performed at this point.

%Lehman's - RQ3
The analysis of the trends and the changes, combined with information gathered during the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's laws are applicable to the changes to the API \cite{lehman1980programs}.

%RQ2
The final stage of analysis was conducted once all the data had been analysed, which allowed us to answer \textbf{RQ2}. This was accomplished by comparing our analysis and interpretation of the change motives against the opinions expressed during the interview. Success was determined by the amount of correct interpretations made about the motives of the changes. Our ability to correctly predict the motives, compared to the designers' actual motives which were made clear during the interviews, served as the basis for answering \textbf{RQ2}.

>>>>

The study was conducted in two major phases \cite{andersson2007spiral}. The aim of the first phase was to generate hyptheses and to formulate clear research questions. This was achieved by using a data-driven approach to analysing the code and documentation. The second phase included analysis of the interviews, during which we aimed to confirm the hypotheses that were formulated in the first phsae. Both phases were performed iteratively. This created the opportunity to improve the data analysis as the study progressed, as well as allowing us to adapt to possible changes in direction, due to the hypothesis generating approach of the first phase.

The process used for examining the code and documentation was inspired by grounded theory analysis \cite{seaman1999qualitative}, as it is recommended for hypothesis generating studies \cite{runeson2009guidelines} \cite{seaman1999qualitative}.

\subsection{Data Collection} \label{data_collection}  
%Intro to code inspection
The data were collected primarily through inspections of the source code and the analysis of accompanying documentation. The source code was comprised of the two API versions previously mentioned. Each version of the API had its own respective documentation, including example code, a library description and a basic development manual.

@@

\subsection{Data Analysis} \label{data_analysis}

%Codes
To analyse the data each change identified in the spreadsheet was coded based on which module the change occurred in and two other characteristics: a) if the change added, removed or modified functionality, and b) if the change was a cosmetic change or not.
%Concepts
Grouping the codes by module allowed us to form general concepts of change. However, changes that affected the whole API were categorised on their own.
%Categories
These concepts were then grouped into categories based on common patterns between the concepts.
%Theory
These categories were then used to identify the most notable trends in the evolution of the API. These trends were later used as a basis for discussion during the interview.

%RQ1
The trends identified previously were then classified according to the software maintenance types \cite{chapin2001types}. The process followed the decision tree used for classifying the types of software evolution and software maintenance \cite{chapin2001types}. Each of the previously identified trends were given a main type of maintenance and, if appropriate, a secondary type. This material, as well as the results of the interview, were then used as the basis for answering \textbf{RQ1}.

%RQ2
To allow us to answer \textbf{RQ2}, we compared our analysis and interpretation of the trends identified prior, against what was expressed by the API architect, during the interview. Success was determined by comparing the inter-rater reliability, by performing calculating Cohen's Kappa gathered data.

%RQ3
The analysis of the changes and trends, combined with the information gathered from the interview, allowed us to answer \textbf{RQ3} by determining if Lehman's Laws apply to the changes made to the API.
